%%%%%%%%%%%%%%%%%
% This is an sample CV template created using altacv.cls
% (v1.1.4, 27 July 2018) written by LianTze Lim (liantze@gmail.com). Now compiles with pdfLaTeX, XeLaTeX and LuaLaTeX.
% 
%% It may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License, either version 1.3
%% of this license or (at your option) any later version.
%% The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.3 or later is part of all distributions of LaTeX
%% version 2003/12/01 or later.
%%%%%%%%%%%%%%%%

%% If you need to pass whatever options to xcolor
\PassOptionsToPackage{dvipsnames}{xcolor}

%% If you are using \orcid or academicons
%% icons, make sure you have the academicons 
%% option here, and compile with XeLaTeX
%% or LuaLaTeX.
% \documentclass[10pt,a4paper,academicons]{altacv}

%% Use the "normalphoto" option if you want a normal photo instead of cropped to a circle
% \documentclass[10pt,a4paper,normalphoto]{altacv}

\documentclass[10pt,a4paper]{altacv}
%% AltaCV uses the fontawesome and academicon fonts
%% and packages. 
%% See texdoc.net/pkg/fontawecome and http://texdoc.net/pkg/academicons for full list of symbols.
%% 
%% Compile with LuaLaTeX for best results. If you
%% want to use XeLaTeX, you may need to install
%% Academicons.ttf in your operating system's font 
%% folder.


% Change the page layout if you need to
\geometry{left=1cm,right=9cm,marginparwidth=6.8cm,marginparsep=1.2cm,top=1.25cm,bottom=1.25cm,footskip=2\baselineskip}

% Change the font if you want to.

% If using pdflatex:
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[default]{lato}

% If using xelatex or lualatex:
% \setmainfont{Lato}

% Change the colours if you want to
\definecolor{Navy}{HTML}{000080}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{heading}{Navy}
\colorlet{accent}{Navy}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}


% Change the bullets for itemize and rating marker
% for \cvskill if you want to
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}
%% sample.bib contains your publications
\addbibresource{sample.bib}

\usepackage[colorlinks]{hyperref}

\begin{document}

\name{Christian Lussier}
\tagline{Computer Science Student}
\personalinfo{%
  % Not all of these are required!
  % You can add your own with \printinfo{symbol}{detail}
  \email{lussierc@allegheny.edu}
  \phone{412-748-0404}
%  \homepage{www.homepage.com}
%  \twitter{@twitterhandle}
  \homepage{www.christianlussier.com}
  \github{https://github.com/lussierc}
  %% You MUST add the academicons option to \documentclass, then compile with LuaLaTeX or XeLaTeX, if you want to use \orcid or other academicons commands.
%   \orcid{orcid.org/0000-0000-0000-0000}
}

%% Make the header extend all the way to the right, if you want. 
\begin{fullwidth}
\makecvheader
\end{fullwidth}

%% Depending on your tastes, you may want to make fonts of itemize environments slightly smaller
% \AtBeginEnvironment{itemize}{\small}


%% Provide the file name containing the sidebar contents as an optional parameter to \cvsection.
%% You can always just use \marginpar{...} if you do
%% not need to align the top of the contents to any
%% \cvsection title in the "main" bar.
\cvsection[page1sidebar]{Experience}

\cvevent{Computer Science Teaching Assistant}{Allegheny College Department of Computer Science}{August 2018 -- Present}{Meadville, PA}
\begin{itemize}
\item Assist students in weekly laboratory sessions and office hours by providing technical support, explaining core concepts, debugging code, fixing software issues, and more.
\item Help in classes involving Python programming, data analytics, database systems, software engineering, algorithms, and Java programming.
\end{itemize}

\divider

\cvevent{Mozilla Fellow}{Allegheny College Department of Computer Science}{August 2020 -- Present}{Meadville, PA}
\begin{itemize}
\item Complete software engineering tasks and help design assignments for upcoming Allegheny College courses that explored biases in the field of Computer Science and beyond.
\end{itemize}

\divider

\cvevent{Student Office Assistant}{Allegheny College Registrar's Office}{September 2018 -- August 2020}{Meadville, PA}
\begin{itemize}
\item Helped the Allegheny College Registrar's office with daily tasks.
\item Organized student files, ran errands, utilized proper professional office phone protocols, and completed other common office tasks.
\end{itemize}

\divider

\cvevent{Electronics Team Member}{Target}{July 2016 - Present}{Gibsonia, PA}
\begin{itemize}
\item Provide a great shopping experience for guests in the electronics department.
\item Train new team members as an electronics trainer.
\item Cross-trained throughout the store and am proficient in any position.
\end{itemize}

\cvsection{Education}

\cvevent{B.S. in Computer Science}{Allegheny College}{May 2021}{}
\begin{itemize}
\item Majoring in Computer Science and minoring in Economics.
\item Hold an overall GPA of 3.82 and a major GPA of 3.99.
\item Took courses such as Software Engineering, Web Development, Data Analytics, Database Systems, Compiler Development, Artificial Intelligence, and more.
\end{itemize}
\medskip


\end{document}
