
\cvsection{Skills}

\cvtag{Python}
\cvtag{Java}
\cvtag{HTML}
\cvtag{CSS}
\cvtag{JS}
\cvtag{R}
\cvtag{C}
\cvtag{SQLite3}
\cvtag{GitHub}
\cvtag{Docker}
\cvtag{Algorithms}
\cvtag{Flask}
\cvtag{CS Concepts}
\cvtag{Customer Service}
\cvtag{Data Analysis}
\cvtag{Data Management}
\cvtag{Git Flow}
\cvtag{SQL}


\cvsection{Notable Projects}
\begin{itemize}

\item \textbf{Senior Thesis - Stock Prediction:}
\begin{itemize}
    \item Researched, implemented, trained, and tested seven different machine learning models with different sizes of data to see how accurate they were in predicting next-day stock price swings.
\end{itemize}

\item \textbf{Cogitate:}
\begin{itemize}
    \item Led the Web Development team and was a software design architect.
    \item Collaboratively created a tool using Python that evaluates the work completed by members of a GitHub repository and generates a contribution score based on metrics.
\end{itemize}

\item \textbf{Petition-Pronto:}
\begin{itemize}
    \item Led team that implemented a tool whereby students could submit academic petitions to department faculties.
    \item I took responsibility for implementing the entire backend of the tool in Flask and configuring the SQLite3 database.
\end{itemize}
\end{itemize}



%\divider\smallskip



\cvsection{Notable Honors}
\begin{itemize}
\item Awarded the Allegheny Student Chapter Prize in recognition of having the best Senior Thesis in Computer Science, as determined by the department's faculty.
\item 1st Place Winner of the Allegheny College 2020 CBE Financial Literacy Challenge.
\end{itemize}

\cvsection{Extracurriculars}
\begin{itemize}
\item \textbf{Vice President \& Treasurer}, \textit{Allegheny College Ice Hockey Club}:

\begin{itemize}
    \item Managed a \$17K yearly budget and run team social media outlets.
    \item Volunteer coach with the Little Penguins ''Learn to Play Hockey`` program at local rink.
\end{itemize}

\item \textbf{Former Officer}, \textit{Allegheny Chapter of ACM}
\end{itemize}




