%% The resume for Christian L. Lussier
% This resume is a modified version of a template by Xavier Danaux (xdanaux@gmail.com).
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c, available at http://www.latex-project.org/lppl/.
% Feel free to modify this resume for your own, please change all of my information on it & follow the liscense listed above.


\documentclass[11pt,a4paper,sans]{moderncv}

% modern theme info
\moderncvstyle{banking}
\moderncvcolor{black}

% package info
\usepackage[utf8]{inputenc}
\usepackage[scale=0.75]{geometry}
\usepackage{import}
\usepackage{multibib,comment}

% important info
\name{Christian}{Lussier}
\address{Address Goes Here} % Enter your address here, I have not put my full address for privacy reasons
\phone{000-000-0000} % Enter your phone number here, I have removed mine for privacy reasons
\email{lussierc@allegheny.edu} % email
\social[github]{lussierc} % github
\homepage{christianlussier.com} % website

% Begin the Document:
\begin{document}
\makecvtitle
\vspace*{-12mm} % Removes whitespace between header and first section (education)
% Objective/Summary Section
% Un-comment the line below and type your summary between the {}'s if wanted.'
%\small{Type objective/summary here.}



% ---------- Begin Resume Main Content ----------

% ------ Begin Education Section: ------
\section{Education}

\vspace{2pt}

\begin{itemize} %Begin experience list
\item{\cventry{May 2021}{Bachelor of Science in Computer Science, Economics}{Allegheny College}{Meadville, PA}{\textit{}}{Cumulative GPA of 3.8/4.0. Named a "Distinguished Alden Scholar" (Deans List).}}
\end{itemize} % End experience list
%------------------------------------------------


% ------ Begin Experience Section: ------
\section{Work Experience}

\vspace{2pt}

\begin{itemize} % Begin Experience List
\item{\cventry{August 2018 - Present}{Teaching Assistant - Department of Computer Science}{Allegheny College}{Meadville, PA}{}{\vspace{3pt}Assist students with laboratory assignments and explain computer science concepts.}}
\vspace{2pt}
\item{\cventry{August 2018 - Present}{Student Assistant - Registrar's Office}{Allegheny College}{Meadville, PA}{}{\vspace{3pt}Assist the Registrar's office with daily office tasks.}}
\vspace{2pt}
\item{\cventry{July 2016 - Present}{Electronics Team Member}{Target}{Gibsonia, PA}{}{\vspace{3pt}Train new team members and provide assistance to guests in the electronics department.}}
\end{itemize} % End experience list
%------------------------------------------------


% ------ Begin Skills Section: ------
\section{Skills}

\vspace{2pt}

\begin{itemize} %Begin Skills list
\item \textbf{Programming Languages:} Proficient in Java, Python, HTML, R, and LaTeX.
\vspace{2pt}
\item \textbf{Industry Skills:} Basic CS concepts, customer service, teamwork, etc.
\end{itemize} % End skills list
%------------------------------------------------


% ------ Begin Projects Section: ------
\section{Notable Projects}

\vspace{2pt}

\begin{itemize} % Begin projects list
\item \textbf{Simple Performance Experiments:}
\begin{itemize} % Begin Simple Performance Experiments info list
  \item Completes performance analyses for user-selected computations and doubling-experiment lengths. Created exclusively in Java.
\end{itemize} % End Simple Performance Experiments info lis
\vspace{2pt}
\item \textbf{Personal Website:}
\begin{itemize} % Begin Website info list
  \item Made personal website in HTML and CSS to showcase myself and my work.
\end{itemize} % End Website info lis
\end{itemize} % End projects list
%------------------------------------------------


% ------ Begin Interests Section: ------
\section{Interests and extracurricular activities}
\vspace{2pt}

\begin{itemize} %%% Begin list of interests & extra-curriculars
\item \textbf{Treasurer,} \textit{Allegheny College Ice Hockey Club:}
\begin{itemize} % Begin Hockey info list
  \item Manage a \$15,000 yearly budget for the school's ice hockey club.
  \item Volunteer coach with the Little Penguins "Learn to Play Hockey" Program at local rink.
  \item Participate in the team's 2 practices and one game a week as a player.
\end{itemize} % End Hockey Info List

\vspace{2pt}

\item \textbf{Officer,} \textit{Allegheny Chapter - Association for Computing Machinery (ACM): }
\begin{itemize} % Begin ACM info list
  \item Assist with event planning, setup, management, and other club activities.
\end{itemize} % End ACM info list
\end{itemize} %%% End list of interests & extra-curriculars
%------------------------------------------------

\end{document} % ends the document
% END OF FILE
