%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{banking}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{black}                                % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\name{Christian}{Lussier}

\address{1788 Constitution Blvd., Valencia, PA 16059}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
\phone[mobile]{412-748-0404}                   % optional, remove / comment the line if not wanted
\email{lussierc@allegheny.edu}                               % optional, remove / comment the line if not wanted
\homepage{www.christianlussier.com}                         % optional, remove / comment the line if not wanted
\social[github]{lussierc} % github
\vspace*{-12mm} % Removes whitespace between header and first section (education)


% to show numerical labels in the bibliography (default is to show no labels); only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}% CONSIDER REPLACING THE ABOVE BY THIS

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%-----       letter       ---------------------------------------------------------
% recipient data
\recipient{ScienceLogic}{}
\date{January 30, 2020}
\opening{Dear Hiring Team,}
\closing{Sincerely,}

\makelettertitle

I am eager to submit my materials for consideration for the Software Engineer Intern, Python position. I found out about this opportunity when I received an email from Allegheny's Computer Science Department about internships at ScienceLogic.

As a junior at Allegheny College, I have learned a variety of technical, communication, and leadership skills that I believe will translate well into the workplace. Through my coursework, I have learned how to utilize tools such as GitHub, R Studio, Django, and Sqlite3. I have also gained experience in using programming languages like Python, Java, C, HTML, and R. I have utilized these tools in a variety of team projects throughout my courses and have gained the valuable experience of working in and leading a team to create fully-functional software ahead of schedule. Last semester, I led a team in the creation of software that will allow students to submit academic petitions to their respective department's faculty at Allegheny College. Outside of class, I have also taken steps to expand my skillset. As the treasurer for Allegheny College’s Ice Hockey Club, I manage a \$17,000 budget, communicate with the league office, and run the team's social media outlets. Also, last year as an Officer in the Allegheny College Chapter of the Association for Computing Machinery, I helped to lead the club, set up events, and communicate with other officers regularly. These roles have greatly strengthened my leadership, teamwork, and communication skills.

I have also demonstrated professionalism and have gained technical and communication skills in my position as a Teaching Assistant for the Allegheny College Department of Computer Science. In this role, I assist students in weekly laboratory sessions by explaining key programming concepts and by helping them better understand and utilize tools such as GitHub, Python, and Java. In addition to this, my work at Target as an electronics team member has taught me how to work in a fast-paced team environment. As a trainer, I have often been called upon to train new team members throughout the store and assist guests during busy times, such as Black Friday and Christmas. This role has given me a better understanding of the customer service experience and has taught me how to better handle pressure in a fast-paced work environment, experiences that I feel could be an asset for this position.

Thank you for taking the time to review my materials and consider my application for the Software Engineer Intern, Python position. I hope to have the opportunity to discuss my interest in the position and qualifications with you further. I am available at your convenience and can be contacted by phone at (412)-748-0404 or by e-mail at lussierc@allegheny.edu. I look forward to hearing from you soon.

\bigbreak
\makeletterclosing
\end{document}


%% end of file `template.tex'.
